Supplementary Information

### 2020-05-25 doc/manuscript/MEE_manuscript.Rmd
trivial typo fix

**Here, develop a new method that allows simultaneous consideration of the effects of tree size, objectively determined principle climate drivers, and other environemntal drivers on annual tree growth.** 
This allows us to ask:
(1) How do radial growth and aboveground biomass increments ($\Delta AGB$) vary with DBH?
(2) What are the most important climate drivers of annual growth, and over which time windows?
(3) What is the shape of the relationship between annual growth and climate drivers?
(4) Are there interactions between DBH and climate drivers common?
(5) How is growth simultaneously influenced by DBH, climate, and other environemental drivers (CO2, atmospheric deposition)?

@@

### Discussion
**We present a new method that allows simultaneous consideration of the effects of tree size, objectively determined principle climate drivers, and other environemntal drivers on annual tree growth.**
Results are broadly consistent with those obtained by traditional methods, but offer several new insights.

>>>>

**Here, develop a new method that allows simultaneous consideration of the effects of tree size, objectively determined principal climate drivers, and other environemntal drivers on annual tree growth.** 
This allows us to ask:
(1) How do radial growth and aboveground biomass increments ($\Delta AGB$) vary with DBH?
(2) What are the most important climate drivers of annual growth, and over which time windows?
(3) What is the shape of the relationship between annual growth and climate drivers?
(4) Are there interactions between DBH and climate drivers common?
(5) How is growth simultaneously influenced by DBH, climate, and other environemental drivers (CO2, atmospheric deposition)?

@@

### Discussion
**We present a new method that allows simultaneous consideration of the effects of tree size, objectively determined principal climate drivers, and other environemntal drivers on annual tree growth.**
Results are broadly consistent with those obtained by traditional methods, but offer several new insights.
